---
title: "Kagumba Family Tree"
author: "<center>Wyclife Agumba Oluoch (wyclifeoluoch@gmail.com) </center>"
date: "<center>`r Sys.time()`</center>"
bibliography: 
  - bib/packages.bib
nocite: '@*'
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
packages <- c("base",
              'knitr',
              'rmarkdown',
              'tidyverse',
              'networkD3')
installed_packages <- packages %in% rownames(installed.packages())
if(any(installed_packages == FALSE)){
  install.packages(packages[!installed_packages])
}
lapply(packages, library, character.only = TRUE) |> invisible()
```

```{r write_bib, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
knitr::write_bib(c(
  .packages(), packages
), 'bib/packages.bib')
```

# Introduction

Kagumba is a great family located in Western Kenya, Kisumu County, Nyando Sub-County, East Kano Location, Katolo Sub-Location, Yogo Village. The family has a long history which I will keep updating from time to time. However, at the moment, I am delighted to create family tree and will give more information later as a weekly update. Keep checking back. ![Here ir is](Rplot.bmp)


```{r}
kagumba_links <- read.csv('D:/JUNK/kag.csv')
kagumba_links$value <- 1
head(kagumba_links)

kagumba_nodes <- data.frame(name = c(as.character(kagumba_links$source),
                                              as.character(kagumba_links$target)) %>% unique())
kagumba_links$IDsource <- match(kagumba_links$source, kagumba_nodes$name)-1 
kagumba_links$IDtarget <- match(kagumba_links$target, kagumba_nodes$name)-1

ColourScal ='d3.scaleOrdinal() .range(["#FDE725FF","#B4DE2CFF","#6DCD59FF","#35B779FF","#1F9E89FF",
"#26828EFF","#31688EFF","#3E4A89FF","#482878FF","#440154FF"])'

sankeyNetwork(Links = kagumba_links, Nodes = kagumba_nodes,
              Source = "IDsource", Target = "IDtarget",
              Value = "value", NodeID = "name", 
              sinksRight=FALSE, colourScale = ColourScal, nodeWidth = 50, fontSize = 24, nodePadding = 20)

```

# References

